

The objective is to "maximize the chance of success for each group" on the class project. The variables that I chose for enhancing the chance of success for each group are how the students in each group have done well in Homework, presentation and how much work experience they have.

Objective function:  maximize chance of success = Z
Decision Variables that lead to success: Homework, Presentation and Work experience

Homework= X1    Work experience= X3    Presentation= X2     

The higher the amount of X1,X2 and X3 are, the more successful a group in the project is. Lets assume all these variable generate equally a unit success of 5:

Z: 5X1 + 5X2 + 5X3

Each student is able to get a score between 1 to 5 for each variable.


```{r}

# Group 1: 

# Student 1: 5 X11+ 3 X12+ 4 X13 =< 50 (50 is the total or maximum grade which each                                           student can aquire ffom all variables)
# Student 2: 4 X21+ 5 X22+ 3 X13 =< 50
# Student 3: 4 X31+ 4 X32+ 4 X33 =< 50


library(lpSolveAPI)

A <- make.lp(3, 3)

# objective function 

set.objfn(A, c(5,5,5))
lp.control(A, sense='max')


# Subject to

set.column(A, 1, c(5,4,4))
set.column(A, 2, c(3,4,5))
set.column(A, 3, c(4,3,4))

set.rhs(A, c(50, 50, 50))
set.constr.type(A, rep("<=",3))

A

solve(A)
get.objective(A)
get.variables(A)


```



```{r}

# Group 2: 

# Student 4: 3 X41+ 3 X42+ 4 X43 =< 50
# Student 5: 3 X51+ 4 X52+ 3 X53 =< 50
# Student 6: 3 X61+ 3 X62+ 3 X63 =< 50



B <- make.lp(3, 3)

# objective function 

set.objfn(B, c(5,5,5))
lp.control(B, sense='max')


# Subject to

set.column(B, 1, c(3,3,3))
set.column(B, 2, c(3,4,3))
set.column(B, 3, c(4,3,3))

set.rhs(B, c(50, 50, 50))
set.constr.type(B, rep("<=",3))

B

solve(B)
get.objective(B)
get.variables(B)

```




```{r}

# Group 3: 

# St 7: 4 X71+ 3 X72+ 4 X73 =< 50
# St 8: 4 X71+ 5 X72+ 4 X73 =< 50
# St 9: 4 X71+ 2 X72+ 3 X73 =< 50

C <- make.lp(3, 3)

# objective function 

set.objfn(C, c(5,5,5))
lp.control(C, sense='max')


# Subject to

set.column(C, 1, c(4,4,4))
set.column(C, 2, c(3,5,2))
set.column(C, 3, c(4,4,3))

set.rhs(C, c(50, 50, 50))
set.constr.type(C, rep("<=",3))

C

solve(C)
get.objective(C)
get.variables(C)


```



```{r}

# Group 4: 

# Student 10: 4 X101+ 3 X102+ 5 X103 =< 50
# Student 11: 4 X111+ 5 X112+ 4 X113 =< 50
# Student 12: 2 X121+ 3 X122+ 2 X123 =< 50

D <- make.lp(3, 3)

# objective function 

set.objfn(D, c(5,5,5))
lp.control(D, sense='max')


# Subject to

set.column(D, 1, c(4,4,2))
set.column(D, 2, c(3,5,3))
set.column(D, 3, c(5,4,2))

set.rhs(D, c(50, 50, 50))
set.constr.type(D, rep("<=",3))

D

solve(D)
get.objective(D)
get.variables(D)


```








